Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-06 paper/paper.tex
confusion matrix; POS tagger

@@

@@

\item[POS $n$-grams] The number of POS 1-, 2-, and 3-grams. 53.92\%.

@@

@@

\section*{Acknowledgments}
This research was supported by a grant from the Israeli Ministry of
Science and Technology.

>>>>

\usepackage{array}

@@

\nss{shouldn't we use the official bib style file instead of natbib?}

@@

\item[POS $n$-grams] All essays were tagged with the Stanford part-of-speech tagger \citep{toutanova-03}.
Features were extracted to count every POS 1-, 2-, and 3-gram in each document. 53.92\%.

@@

\begin{table*}\small\centering
\begin{tabular}{>{\bf}l|r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r@{ }r|ccc} %from the email sent by the organizers
	& \bf ARA & \bf CHI & \bf FRE & \bf GER & \bf HIN & \bf ITA & \bf JPN & \bf KOR & \bf SPA & \bf TEL & \bf TUR & \bf Precision (\%) & \bf Recall (\%) & \bf $F_1$ (\%) \\
\hline
ARA & 80 & 0 & 2 & 1 & 3 & 4 & 1 & 0 & 4 & 2 & 3 & 80.8 & 80.0 & 80.4 \\
CHI & 3 & 80 & 0 & 1 & 1 & 0 & 6 & 7 & 1 & 0 & 1 & 88.9 & 80.0 & 84.2 \\
FRE & 2 & 2 & 81 & 5 & 1 & 2 & 1 & 0 & 3 & 0 & 3 & 86.2 & 81.0 & 83.5 \\
\hline
GER & 1 & 1 & 1 & 93 & 0 & 0 & 0 & 1 & 1 & 0 & 2 & 87.7 & 93.0 & 90.3 \\
HIN & 2 & 0 & 0 & 1 & 77 & 1 & 0 & 1 & 5 & 9 & 4 & 74.8 & 77.0 & 75.9 \\
ITA & 2 & 0 & 3 & 1 & 1 & 87 & 1 & 0 & 3 & 0 & 2 & 82.1 & 87.0 & 84.5 \\
\hline
JPN & 2 & 1 & 1 & 2 & 0 & 1 & 87 & 5 & 0 & 0 & 1 & 78.4 & 87.0 & 82.5 \\
KOR & 1 & 5 & 2 & 0 & 1 & 0 & 9 & 81 & 1 & 0 & 0 & 80.2 & 81.0 & 80.6 \\
SPA & 2 & 0 & 2 & 0 & 1 & 8 & 2 & 1 & 78 & 1 & 5 & 77.2 & 78.0 & 77.6 \\
\hline
TEL & 0 & 1 & 0 & 0 & 18 & 1 & 2 & 1 & 1 & 73 & 3 & 85.9 & 73.0 & 78.9 \\
TUR & 4 & 0 & 2 & 2 & 0 & 2 & 2 & 4 & 4 & 0 & 80 & 76.9 & 80.0 & 78.4 \\
\end{tabular}
\caption{Official test set confusion matrix with the full model. \nss{which direction is predicted vs. gold?}
Accuracy is 81.5\%.}\label{tbl:matrix}
\end{table*}

@@

\section*{Acknowledgments}
This research was supported by a grant from the Israeli Ministry of
Science and Technology.\nss{anything from the CMU side?}
